\documentclass[11pt]{article}

\usepackage{graphicx}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in


\title{ Robert Soul\'{e} Career Summary}
\author{  }
\date{ }

\begin{document}

\maketitle	
\thispagestyle{empty}


Robert Soul\'{e} is an Associate Professor in the Department of
Computer Science at Yale University, with a joint appointment in the
Department of Electrical Engineering. Prior to joining Yale, he was an
Associate Professor in the Faculty of Informatics at the
Universit\`{a} della Svizzera italiana in Lugano, Switzerland, where
he still holds an Adjunct Professor position.


Professor Soul\'{e} is well-known in the computer networking community
for his work on programmable networks, particularly for his
foundational contributions to in-network computing. He was strongly
involved in the development of the P4 programming language, the
Barefoot Tofino Programmable Switch Chip, and the development of
applications that used those technologies.  His work was among the
first to propose pushing traditional application logic into
programmable switches, achieving significant performance improvements
and drawing into question the long-standing assumptions about the
division of labor between applications and the network.

He has conducted research on a broad range of topics in computer
systems, including networking, distributed systems, databases, and
programming languages. His most recent work has focused on
energy-efficiency, the formal specification of quantum networks,
synchronous consensus protocols, and improving the observability
of operating system state.


Professor Soul\'{e} is a Senior Member of the ACM and IEEE. His work
has been recognized with numberous awards, including best paper awards
at ACM DEBS 2012, NSDI 2018, and CoNEXT 2020, as well as the 2019
SIGMETRICS Highlights Beyond Sigmetrics. Recently, he was a recipient
of the 2025 SIGCOMM Networking Systems Award for his contributions to
the Barefoot Tofino Programmable Switch Chips and the P4 Programming
Language.


He has held several technical leadership positions, including
serving as a member of the P4 Technical Steering Team and a chair of
the P4 Education Working Group. He has held consulting positions in
industry at Barefoot Networks, Intel Corporation, and most recently,
Cerebras Systems, where he works on the network architecture for their
AI inference and training data centers.

He regularly serves on technical program committees for top systems
conferences, including NSDI, SIGCOMM, OSDI, and EuroSys. He has
organized three refereed tutorials at SIGCOMM and one at NSDI.


Professor Soul\'{e} received a Ph.D. from New York University and a
B.A. from Brown University. After completeing his Ph.D., he was a
post-doctoral associate at Cornell University. Prior to pursuing a
career in academia, he worked at several companies in industry,
including Morgan Stanly, Bloomberg, and LimeWire.







\end{document}
